DraftOne

### 2016-06-23 DraftOne.Rmd

```{r}
constant_baseline <- function(n, lambda, start.date = "2000-01-01", ...){
        start.date <- as.Date(start.date)
        date <- seq(from = start.date, by = 1, length.out = n)
        exp_base_y <- rep(lambda, n)
        df <- data.frame(date = date,
                         exp_base_y = exp_base_y)
        return(df)
}
constant_baseline(n = 3, lambda = 100)
```

@@

```{r}
calc_t 
```

@@

```{r}
# A function for binary exposure which varies by season:
season_binexp

# A function for continuous exposure which varies by season:
season_contexp
```

>>>>

```{r}
constant_baseline 
constant_baseline(n = 3, lambda = 100)
```

@@

```{r}
calc_t
calc_t(n=10, trend="curvilinear")
```

@@

```{r}
# A function for binary exposure which varies by season:
season_binexp
season_binexp(n=100, p=.25)

# A function for continuous exposure which varies by season:
season_contexp
season_contexp(10, mu = 100, sd = 10, trend = "curvilinear")
```
